Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-05-05 PAPER/main.tex
started MFFD+ section, added average speeds to comparison, changed figure 1

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
	\caption{Dimensions of an item $i \in \mathcal{I}$, and knives mounted on a bar score two items simultaneously.}	
	\label{fig:itemsknife}
\end{figure}

@@

\section{Solving the SCSPP}
\label{sec:scsppsoln}

\begin{definition}
	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e. $\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$). Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

\subsection{Modified First-Fit Decreasing with AHCA (MFFD$^+$)}
\label{sec:mffd+}
\begin{itemize}
	\item Like original FFD, sort items in non-increasing order, and attempt to pack each item into first strip that can feasibly accommodate the item without exceeding capacity
	\item if item can fit onto strip, apply AHCA on all items on the strip and the current item to find a feasible alignment of the items
	\item if solution found, place the items on the strip in the order of the solution
	\item if no solution found, no feasible alignment exists, attempt to place current item on next strip
	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found
	\item Unlike in Basic FFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in Basic FFD
	\item Slower as AHCA must be run for each item that can fit on a strip
	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in Basic FFD heuristic as VSC is not met in either orientation of the item, whereas by using FFD+ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
\end{itemize}

@@

\section{Comparison}
\begin{itemize}
	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item changing the value of $\tau$ changes the proportion of the number of score widths
	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
	\item As the strip length is decreased, ffd+ improves, number of items/strip decreases
	\item when $\delta = 1.0$ basicffd and ffd+ will perform in the same manner (standard ffd)
	\item Pairsmallest does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
\end{itemize}

@@

\textbf{$n$ = 100}
\begin{itemize}
	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829
	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618
	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703 
\end{itemize}

\textbf{$n$ = 500}
\begin{itemize}
	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227
	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150
	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041 
\end{itemize}

\textbf{$n$ = 1000}
\begin{itemize}
	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463
	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734
	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895 
\end{itemize}

>>>>

\begin{figure}[h!]	
	\centering
	\includestandalone[width=0.8\textwidth]{figures/itemsknife}
	\caption{Dimensions of an item $i \in \mathcal{I}$ in a regular orientation, and a feasible alignment of two items that can be scored simultaneously.}	
	\label{fig:itemsknife}
\end{figure}

@@

\section{Heuristics for the SCSPP}
\label{sec:scsppsoln}

\begin{definition}
	\label{defn:subprob}
	Let $\mathcal{I}' \subseteq \mathcal{I}$ be a set of items whose total width is less than or equal to the capacity of a strip, (i.e. $\sum_{i=1}^{|\mathcal{I}'|}w_i \leq W$). Given a minimum scoring distance $\tau$, the Score-Constrained Packing Sub-Problem (SCPSP) involves finding an arrangement of the items in $\mathcal{I}'$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

\subsection{Modified First-Fit Decreasing with AHCA (MFFD$^+$)}
\label{sec:mffd+}

The last heuristic incorporates AHCA as described in Section \ref{sec:ahca}. The \textsc{Modified First-Fit Decreasing with AHCA} (MFFD$^+$) heuristic operates in a similar fashion to the MFFD, placing items sorted in decreasing order onto the lowest-indexed strip. However, when the lowest-indexed strip is found that can accommodate the current item, MFFD$^+$ then executes AHCA on the sub-problem, where the items on the strip and the current item form the subset $\mathcal{I}' \subseteq \mathcal{I}$. If AHCA finds a feasible solution, the items are placed on the strip in the order of the solution, which includes the current item, else MFFD$^+$ attempts to pack the current item on the next lowest-indexed strip.

\begin{itemize}
	\item Like original FFD, sort items in non-increasing order, and attempt to pack each item into first strip that can feasibly accommodate the item without exceeding capacity
	\item if item can fit onto strip, apply AHCA on all items on the strip and the current item to find a feasible alignment of the items
	\item if solution found, place the items on the strip in the order of the solution
	\item if no solution found, no feasible alignment exists, attempt to place current item on next strip
	\item Using AHCA means if a feasible alignment of items inc current items exists (i.e. VSC is met between all items on strip), it will be found (guaranteed)
	\item Unlike in MFFD where an item cannot be placed on the end because VSC is not met, here we can find a solution
	\item items may potentially be entirely rearranged, not in non-decreasing order on each strip as in MFFD (refer to Figure \ref{fig:comparestrips})
	\item Slower as AHCA must be run for each item that can fit on a strip
	\item see Figure \ref{fig:comparestrips}, item cannot be placed onto strip in MFFD heuristic as VSC is not met in either orientation of the item, whereas by using MFFD$^+$ a feasible solution can be found, item can be placed, no need to try another strip or start a new strip
	\item each iteration when an item can fit onto the strip, we have an instance of the sub problem, where the items on the strip and the current items are in the subset $\mathcal{I}' \subseteq \mathcal{I}$ Refer to definition \ref{defn:subprob}.
	\item Then run AHCA on the subproblem, ignore all other strips.
	\item worst case is AHCA is performed for each item on every strip in $\mathcal{S}$ so far (except when new strip needs to be started, AHCA isn't performed, item is simply placed in regular orientation at beginning of the strip).
	\item reduces chances of needing to start a new strip, therefore reducing possibility of increasing number of strips in final solution.

\end{itemize}

@@

\section{Comparison}
\begin{itemize}
	\item Heuristics implemented in C++ and executed on a computer equipped with an Intel Core i3-2120 processor with a frequency of 3.30GHz.
	\item $n$ = 100, 500, and 1000, number of items in $\mathcal{I}$, $W$ = 5000, 2500, 1250, item widths uniform dist [150, 1000], score widths uniform dist [1,70] (ensures each item has two score widths that do not overlap), all items and strips have height H ( = 1)
	\item Changing strip length changes the average number of items per strip (why is this important?) Harder problems have fewer items per strip
	\item run each instance 1000 times (per value of $\delta$), same instances each time.
	\item table shows optimality, which is the number of strips in the final solution generated by the heuristic divided by the number of strips in the optimal solution (which is calculated using the lower bound for $k$ above), =1 then optimal
	\item Goulimis stated n= 10, this is able to find solutions for n=1000
	\item graph showing time or optimality of all three heuristics
	\item $\delta$ is proportion of score widths that meet VSC (excluding partners and itself), 0.1 increments.
	\item changing the value of $\tau$ changes the proportion of the number of score widths
	\item if $\delta = 0.0$, then no score widths can be aligned number of strips = $n$, $\delta = 1.0$, then all score widths can be aligned with any other score width, BPP.
	\item As the strip length is decreased, MFFD+ improves, number of items/strip decreases
	\item when $\delta = 1.0$ MFFD and MFFD+ will perform in the same manner (like original FFD)
	\item PS does not reach highest optimality at $\delta = 0.8$ onwards in any strip length
	\item as avg number of items per strip decreases, PS is less efficient, MFFD+ is better
	\item note anomaly in $n = 1000, W = 1250, \delta = 0.3$, MFFD performs the best.
\end{itemize}

@@

\textbf{$n$ = 100}
\begin{itemize}
	\item Average total item width = 57466.776, $\sigma$ = 2499.06092
	\item $W = 5000$, Average LB = 11.993, $\sigma$ = 0.56829, Average speed = 38.88504ms/instance
	\item $W = 2500$, Average LB = 23.478, $\sigma$ = 1.05618, Average speed = 38.55795ms/instance
	\item $W = 1250$, Average LB = 46.466, $\sigma$ = 2.02703, Average speed = 37.98091ms/instance
\end{itemize}

\textbf{$n$ = 500}
\begin{itemize}
	\item Average total item width = 287683.855, $\sigma$ = 5434.63046
	\item $W = 5000$, Average LB = 58.039, $\sigma$ = 1.12227, Average speed = 42.11938ms/instance
	\item $W = 2500$, Average LB = 115.571, $\sigma$ = 2.18150, Average speed = 44.24521ms/instance
	\item $W = 1250$, Average LB = 230.648, $\sigma$ = 4.35041, Average speed = 49.66614ms/instance
\end{itemize}

\textbf{$n$ = 1000}
\begin{itemize}
	\item Average total item width = 575163.174, $\sigma$ = 7880.93401
	\item $W = 5000$, Average LB = 115.534, $\sigma$ = 1.59463, Average speed = 214.04479ms/instance
	\item $W = 2500$, Average LB = 230.563, $\sigma$ = 3.16734, Average speed = 190.36579ms/instance
	\item $W = 1250$, Average LB = 460.623, $\sigma$ = 6.30895, Average speed = 214.78729ms/instance
\end{itemize}
